Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-12-14 manuscript/response_to_reviews.Rmd

Reinmann A. B. & Hutyra L. R. (2017). Edge effects enhance carbon uptake and its vulnerability to climate change in temperate broadleaf forests. Proceedings of the National Academy of Sciences, 114(1), 107–112. https://nam02.safelinks.protection.outlook.com/?url=https%3A%2F%2Fdoi.org%2F10.1073%2Fpnas.1612369114&amp;data=04%7C01%7Cteixeirak%40si.edu%7Cd27c53d6ec434c8ae42108d8a03017cf%7C989b5e2a14e44efe93b78cdd5fc5d11c%7C0%7C0%7C637435475707545147%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C1000&amp;sdata=GncJJ%2FLa2f96c0tjkl5RZZv2JLJFoAoQnOTm0b%2BYyNo%3D&amp;reserved=0.

Reinmann A. B., Smith I. A., Thompson J. R. & Hutyra L. R. (2020). Urbanization and fragmentation mediate temperate forest carbon cycle response to climate. Environmental Research Letters, 15, 114036.

Remy E., Wuyts K., Boeckx P., Ginzburg S., Gundersen P., Demey A., … Verheyen K. (2016). Strong gradients in nitrogen and carbon stocks at temperate forest edges. Forest Ecology and Management, 376(2016), 45–58. https://nam02.safelinks.protection.outlook.com/?url=https%3A%2F%2Fdoi.org%2F10.1016%2Fj.foreco.2016.05.040&amp;data=04%7C01%7Cteixeirak%40si.edu%7Cd27c53d6ec434c8ae42108d8a03017cf%7C989b5e2a14e44efe93b78cdd5fc5d11c%7C0%7C0%7C637435475707545147%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C1000&amp;sdata=u2ylmC4K4VIxHWamrCnk%2BNfu%2FsZDUkSPfABgfN%2BCzT4%3D&amp;reserved=0.

Smith I. A., Hutyra L. R., Reinmann A. B. & Thompson J. R. (2019). Evidence for Edge Enhancements of Soil Respiration in Temperate Forests Geophysical Research Letters. Geophysical Research Letters, 46, 1–10. https://nam02.safelinks.protection.outlook.com/?url=https%3A%2F%2Fdoi.org%2F10.1029%2F2019GL082459&amp;data=04%7C01%7Cteixeirak%40si.edu%7Cd27c53d6ec434c8ae42108d8a03017cf%7C989b5e2a14e44efe93b78cdd5fc5d11c%7C0%7C0%7C637435475707545147%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C1000&amp;sdata=92jjRZSUzQrNX6SGlV%2BZRfHlUN%2B6AL96%2FJIl4PIK3a8%3D&amp;reserved=0.

## References

```{r eval=FALSE, echo=FALSE}
# All references should be presented in alphabetical order and should also be bundled in ways that will help the reader to find those that are germane to each of the themes, topics or issues that the authors have used to organize the review. Such a matrix will be included as supplementary material. ERL has no standardized format for subdividing references by cross-cutting themes, but guidance from editors will be helpful to authors.
```
